Figures for SI

### 2021-07-09 analysis/SI_figs.Rmd
fixed so many things

```{r}
all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources.csv") %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

@@

fao_data <- read_csv("marine/STEP1_species_groups/int/tonnes_per_country_group.csv") %>%
  group_by(country) %>%
  summarise(prod = sum(total_tonnes))
```

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")

@@

## Make the global map (Figure 1)
```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)

@@

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
    #  geom_vline(xintercept = 135) + # check to make sure it lines up
  #geom_hline(yintercept = 0) # check to make sure it lines up

total_map

# guides(colour=guide_legend(nrow=30))

# Create marginal plots
# Use geom_density/histogram for whatever you plotted on x/y axis 
plot_x <- axis_canvas(total_map, axis = "x") +
  geom_histogram(data = all_farms, aes(X, fill = data_type), bins = 360)  +
  #  geom_vline(xintercept = 135) + # check to make sure it lines up
  coord_sf(xlim = c(-180, 180), expand = FALSE) +
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
plot_x

plot_y <- axis_canvas(total_map, axis = "y") +
  geom_histogram(data = all_farms, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
 #  geom_hline(yintercept = 0) + #  check to make sure it lines up
  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
 # coord_flip() 
plot_y

# Combine all plots into one
plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
ggdraw(plot_final)
ggsave("analysis/figs/map_fig.jpg")

@@

## Make finer resolution maps (Figure 2)
```{r}
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)
library(ggpubr)
library(RColorBrewer)
library(ggspatial)
library(ggplot2)
library(patchwork)

## zoomed maps

chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
  # coord_sf(crs = 4326, xlim = c(-75, -72.5), ylim = c(-46, -44), expand = FALSE) +
  theme(legend.position = "bottom", ## put legend on bottom
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("A")  # + 
 #  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))
chl_zoom

## China - near 
chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
#   coord_sf(crs = 4326, xlim = c(120.5, 123), ylim = c(28.5, 30.5), expand = FALSE) + # near Ningbo, in Zhejiang province, near shanghai
  coord_sf(crs = 4326, xlim = c(121.5, 122.75), ylim = c(29.5, 30.5), expand = FALSE) + # part of Zhejiang province
  #coord_sf(crs = 4326) + 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
        legend.key = element_rect(fill = NA),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("D")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
chn_zoom

## Ecuador - Near Guayaquil
ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
  #coord_sf(crs = 4326) + 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("B")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
ecu_zoom

## Norway
nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
  # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
    coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("C")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
nor_zoom

# (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

plot1 <- (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "none") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none"))

plot1 
ggsave("analysis/figs/chl_ecu_zoom.jpg")

plot2 <- (nor_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

plot2
ggsave("analysis/figs/nor_chn_zoom.jpg")

## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder as "zoom_fig_final.jpg"

## Radial bar chart of estimation type per country

```{r}
library(tidyverse)
library(viridis)
library(hrbrthemes)
library(RColorBrewer)
library(colorspace)

rank_rgn <- all_farms %>%
  mutate(country = ifelse(country == "United Kingdom (Scotland) ", "United Kingdom", country)) %>%
  group_by(country) %>%
  summarise(num_farms_total = n()) %>%
  ungroup() %>%
  arrange(num_farms_total)

## Stuff for both plots
# i think that this would look better with each stressor having its own color that is paired with ocean/land
# 
# pick 4 distinct colors and then create a pair with one being more brown or green and the other being more blue

source_name <- data.frame(source = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))

type_1 <- "forestgreen"
type_1 <- lighten(type_1, amount = -0.05)
type_2 <- "orange1"
type_2 <- lighten(type_2, amount = -0.05)
type_3 <- "red3"
type_3 <- lighten(type_3, amount = -0.05)

gc_palette <- c(type_1, type_2, type_3)
scales::show_col(gc_palette, n = 3)

pal_df <- as_tibble(gc_palette) %>% 
  rename(fill_value = value) %>% 
  mutate(source = case_when(fill_value == type_1 ~ "known location",
                            fill_value == type_2 ~ "modeled location, known number of farms",
                            fill_value == type_3 ~ "modeled location, estimated number of farms"))

## circle plot

cutoff_value <-  1000

by_country <- all_farms %>%
  mutate(country = ifelse(country == "United Kingdom (Scotland) ", "United Kingdom", country)) %>%
  group_by(country, data_type) %>%
  summarise(num_farms = n()) %>%
  ungroup() %>%
  group_by(country) %>%
  mutate(num_farms_total = sum(num_farms)) %>%
  ungroup() %>%
  arrange(num_farms_total) %>%
  filter(num_farms_total < cutoff_value)

##grab the highest country to highlight red and id where the circle ends and then side bar chart begins
highest_country <- by_country[dim(by_country)[1], "country"]
farms_highest_country <- filter(by_country, country %in% highest_country$country) #used below

# adjust the rank_rgn-adjust dataframe to match above
rank_rgn_adj <- rank_rgn %>%
  filter(country %in% by_country$country)

# add empty space to create space in the circleplot for axes
 empty_bar <- 5
 to_add <- data.frame(matrix(NA, empty_bar, ncol(rank_rgn_adj)) )
 colnames(to_add) = colnames(rank_rgn_adj)
 to_add$country <- as.character(1:empty_bar)
 rank_rgn_adj  <- rbind(to_add, rank_rgn_adj)

 # some code to orient the country labels
sequence_length = length(unique(rank_rgn_adj$country))
first_sequence = c(1:(sequence_length%/%2)) 
second_sequence = c((sequence_length%/%2+1):sequence_length) 
first_angles = c(90 - 180/length(first_sequence) * first_sequence)
second_angles = c(-90 - 180/length(second_sequence) * second_sequence)
rank_rgn_adj$angle <- c(first_angles, second_angles)
rank_rgn_adj$hjust <- c(rep(0, length(first_sequence)), 
                    rep(1, length(second_sequence)))

# color for region labels
rank_rgn_adj <- rank_rgn_adj %>%
  mutate(country = factor(country, unique(country))) %>%
  mutate(color = "black") %>%
  mutate(color = ifelse(is.na(num_farms_total), "white", color)) %>%
  mutate(color = ifelse(country %in% highest_country$country, "red", color))

## make the plot

circle_theme <- theme(axis.line=element_blank(),
                      axis.text.y=element_blank(),
                      axis.ticks=element_blank(),
                      axis.title.x=element_blank(),
                      axis.title.y=element_blank(),
                      legend.position="none",
                      panel.background=element_blank(),
                      panel.border=element_blank(),
                      panel.grid.major=element_blank(),
                      panel.grid.minor=element_blank(),
                      plot.background=element_blank(),
                      axis.text.x = element_blank())

color_order <- c(type_1, type_2, type_3)

pressures_adj_circle_plot <- by_country %>% 
  mutate(prop_of_global_stacked = abs(num_farms)) %>% 
  left_join(pal_df, by = c("data_type" = "source")) %>% 
  mutate(fill_value = factor(fill_value, levels = color_order))

 ggplot(data=pressures_adj_circle_plot, aes(x=country, y=prop_of_global_stacked, fill = fill_value)) +

  geom_bar(stat="identity") +

  # ## this adjust the inner circle size (ymin) and outer circle size (ymax), which can be expanded to include names
   geom_errorbar(aes(
       x     = 1,
        ymin = -0.01,   # ymin  = -0.03, this is for when ocean bars stack inwards -0.01 for when not
       ymax  = 0.035),
       alpha = 0) +
      # Country name text placement
     geom_text(
       data = rank_rgn_adj,
       aes(x     = country,
           y     = max(by_country$num_farms_total, na.rm=TRUE),
           label = country,
           angle = angle,
           hjust = hjust),
       inherit.aes = FALSE,
       fontface = "bold",
       alpha = 0.9,
       size = 4,
       color = rank_rgn_adj$color) +
    # 
   # georegion names
    # geom_text(
    #   data=rgn_shift,
    #   aes(y = 0.02, x = name_x, label = georegion),
    #   # aes(x=name_x,
    #   #     y=name_y,
    #   #     label=georegion),
    #   inherit.aes=FALSE, size=7) +
  #  
  # # # Scale bar circles
  # ## This adds the 0 line
      geom_segment(
        x = 0, 
         y = 0, 
         xend = dim(rank_rgn_adj)[1]+1, 
         yend = 0, 
         fill = NULL,
        alpha = 1, color = "white", size = 0.1) + #color = "black for internal
  #    
  #  # Scale bar annotation, this adds the y-axis numbers
      annotate("text",
        x     = c(3, 3, 3),
        y     = c(0, 0.0175, 0.035),
        label = c(0, 0.0175, 0.035),
        color = "darkgray", angle = -4, size = 4) +
  #     
  scale_color_identity() +
   scale_fill_identity() +
   # scale_fill_manual(values= rev(myPalette), c("Land: Disturbance", "Land: GHG", "Land: Water", "Land: Nutrient",
   #                                    "Ocean: Disturbance", "Ocean: GHG", "Ocean: Water", "Ocean: Nutrient")) +
  coord_polar() +
 circle_theme

ARCHIVE: Other ways of trying to visualize
```{r}

## philippines
# phl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
#   annotation_map_tile(type = "osm", zoomin = 0) + 
#   geom_spatial_point(size = 1, alpha = 0.7) + 
#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
#   coord_sf(crs = 4326, xlim = c(120.25, 122.5), ylim = c(17, 19), expand = FALSE) +
#   #coord_sf(crs = 4326) + 
#   theme(legend.position = "bottom", 
#         legend.title=element_blank(), 
#         axis.title.x = element_blank(), 
#         axis.title.y = element_blank(),
# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
#   ggtitle("B")
#   #border(linetype = "longdash")
#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
# phl_zoom

## California - bay area 
# cal_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
#   annotation_map_tile(type = "osm", zoomin = 0) + 
#   geom_spatial_point(size = 1, alpha = 0.7) + 
#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
#   coord_sf(crs = 4326, xlim = c(-123, -121), ylim = c(37, 39), expand = FALSE) +
#   #coord_sf(crs = 4326) + 
#   theme(legend.position = "bottom", 
#         legend.title=element_blank(), 
#         axis.title.x = element_blank(), 
#         axis.title.y = element_blank(),
# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
#   ggtitle("B")
#   #border(linetype = "longdash")
#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
# cal_zoom

## New Zealand
# nzl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
#   annotation_map_tile(type = "osm", zoomin = 0) + 
#   geom_spatial_point(size = 0.5, alpha = 0.7) + 
#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
#   # coord_sf(crs = 4326, ylim = c(-48, -34), xlim = c(165, 180), expand = FALSE) + ## all of new zealand
#    coord_sf(crs = 4326, ylim = c(-41, -34), xlim = c(172, 180), expand = FALSE) + ## north island
#   theme(legend.position = "bottom", 
#         legend.title=element_blank(), 
#         axis.title.x = element_blank(), 
#         axis.title.y = element_blank(),
#         axis.text.x = element_text(angle = 60, hjust = 1),
# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
#   ggtitle("D")
#   #border(linetype = "longdash")
#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
# nzl_zoom

## all together
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.2) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(), 
        legend.position = "none") 
total_map

## make longitude histogram

lon_hist <- ggplot(data = all_farms) + 
  geom_histogram(aes(X, fill = data_type), bins = 360) + 
  # scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180)) +
  # scale_y_reverse() +
   theme_void() + 
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(), 
        legend.position = "none") # +
  # geom_vline(xintercept = 135) 
lon_hist

## make latitude histogram
lat_hist <- ggplot(data = all_farms) + 
  geom_histogram(aes(Y, fill = data_type), bins = 180) + 
  # scale_x_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  # xlim(-58, 73) + 
  coord_flip() +
   theme_void() + 
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(), 
        legend.position = "none") # + 
  # geom_vline(xintercept = 0)

lat_hist

require(gridExtra)
library(cowplot)
library(egg)

## using ggExtra
library(ggExtra)
ggExtra::ggMarginal(total_map, type = "histogram", groupFill = TRUE, size = 2)

## using patchwork
lon_hist + plot_spacer() + total_map + lat_hist + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))

## using cowplot
plot_grid(
  lon_hist
  , NULL
  , total_map
  , lat_hist
  , ncol = 2
  , nrow = 2
  , rel_heights = c(0.2, 1)
  , rel_widths = c(1, 0.2)
)

test_data <- all_farms %>%
  filter(data_type != "known location")

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = test_data, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
    #  geom_vline(xintercept = 135) + # check to make sure it lines up
  #geom_hline(yintercept = 0) # check to make sure it lines up

total_map

ggsave("analysis/figs/map_fig_test.jpg")

>>>>

```{r}
all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

@@

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")

@@

## Make the global map by species group (Supplementary Figures 1-6)
```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)

@@

for(i in c(1, 2,3, 6)){

 # i = 4

  spp_group <- unique(all_farms$species_group)[i]

  all_farms_i <- all_farms %>%
    filter(species_group == spp_group)

  count_green_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "known location")

  count_green <- count_green_df$n

  count_yellow_df <-  all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled location, known number of farms")

  count_yellow <- count_yellow_df$n

  count_red_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled location, estimated number of farms")

  count_red  <- count_red_df$n

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank(),
        text=element_text(family="Times New Roman")) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
  # scale_color_manual(values = c("forestgreen", "orange1"),
  #                   breaks = c("known location", "modeled location, known number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow))) + 
    # scale_color_manual(values = c("red3"),
    #                 breaks = c("modeled location, estimated number of farms"), labels = c(sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
  labs(title = sprintf("Supplmentary Figure %s: %s farms", i, spp_group))

# total_map

# Create marginal plots
# Use geom_density/histogram for whatever you plotted on x/y axis 
plot_x <- axis_canvas(total_map, axis = "x") +
  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
  #  geom_vline(xintercept = 135) + # check to make sure it lines up
  coord_sf(xlim = c(-180, 180), expand = FALSE) +
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
plot_x

plot_y <- axis_canvas(total_map, axis = "y") +
  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
 #  geom_hline(yintercept = 0) + #  check to make sure it lines up
  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
 # coord_flip() 
plot_y

# Combine all plots into one
plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
ggdraw(plot_final)

ggsave(sprintf("analysis/figs/supp_map_fig_%s.jpg", spp_group))

}

@@
